---
title: "Code"
author: "Group 6"
output: html_document
---
#import code



```{r read_data}
library(tidyverse)
EugeneHomes <- read_csv("data/EugeneHomes.csv")
```

#means and summary statistics by group

```{r}
library(Rmisc)

sum = summarySE(EugeneHomes,
                measurevar="price",groupvars=c("status","garage"))
sum
```


#interaction plot using summary statistics

```{r}
interaction.plot(x.factor = EugeneHomes$garage, trace.factor = EugeneHomes$status, 
                 response = EugeneHomes$price, fun = mean, 
                 type = "b", legend = TRUE, 
                 xlab = "Number of Garages", ylab="Price of Homes",
                 pch=c(1,19), col = c("#00AFBB", "#E7B800"))
```


#boxplot of each predictor and interaction

```{r}
boxplot(price ~ status,
        data = EugeneHomes,
        xlab = "Status of Homes",
        ylab = "Price of Homes in Thousands")
boxplot(price ~ garage,
        data = EugeneHomes,
        xlab = "Number of Garages in Homes",
        ylab = "Price of Homes in Thousands")
boxplot(price ~ status:garage,
        data = EugeneHomes,
        xlab = "Status x Garage",
        ylab = "Price of Homes")
```


#Fitting Model and Conducting ANOVA (lm is type 2)

```{r}
model = lm(price ~ status + garage + status:garage,
             data = EugeneHomes)
anova(model)
summary(model)
```


#Checking Assumptions

```{r}
hist(residuals(model))
plot(fitted(model),
     residuals(model))
```


#multiple comparisons Bonferroni?

#Corilation
#First, create a subset without variables to right of status

```{r}
library(dplyr)

EugeneHomes = select(EugeneHomes,
                     price,
                        size,
                        lot,
                        bath,
                        bed,
                        bathbed,
                        year,
                        age,
                        agesq,
                        garage,
                        status)
```


#to view new subset dataset with the terms specified

```{r}
library(FSA)

headtail(EugeneHomes)
```


#to view corrilation

```{r}
library(psych)

corr.test(EugeneHomes,
          use = "pairwise", 
          method = "pearson", 
          adjust = "none")
```


#to view scatterplot matrix of all variables against each other

```{r}
pairs(data=EugeneHomes, ~ price + size + lot + bath + bed + bathbed 
      + year + age + agesq + garage + status)
```


#to view correlation with histograms, scatterplots and corrilation
#numbers

```{r}
library(PerformanceAnalytics)

chart.Correlation(EugeneHomes,
                  method="pearson",
                  histogram=TRUE,
                  pch=16)
```


#Stepwise procedure to determine the best regression equation

```{r}
model.null = lm(price ~ 1, data=EugeneHomes)
model.full = lm(price ~ size + lot + bath + bed + bathbed 
                + year + age + agesq + garage + status, 
                data=EugeneHomes)

step(model.null,
     scope = list(upper=model.full),
     direction="both",
     data=EugeneHomes)
```


#Now that we have dropped 2 predictors, we will define the final model
#this shows coefficients, R-squared, and overall p-value

```{r}
model.final = lm(price ~ garage + agesq + lot + status + size
                 + bed + bathbed + bath, data = EugeneHomes)
summary(model.final) 
```


#We can also do our Analysis of Variance for individual terms

```{r}
library(car)

Anova(model.final,
      Type="II")
```


#plot of predicted values with 1-to-1 line

```{r}
EugeneHomes$predy = predict(model.final)

plot(predy ~ price,
     data=EugeneHomes,
     pch = 16,
     xlab="Actual reponse value",
     ylab="PRedicted response value")

abline(0,1, col="blue", lwd=2)
```


#Histogram of Residuals

```{r}
hist(residuals(model.final),col="darkgray")
```


#plot of Fitted vs. Residuals

```{r}
plot(fitted(model.final),
     residuals(model.final))
```



